### 2020-06-04 README.Rmd
README

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/antaldaniel/eurobarometer/branch/master/graph/badge.svg)](https://codecov.io/gh/antaldaniel/eurobarometer?branch=master)
[![Project Status: Minimal or no implementation has been done yet, or the repository is only intended to be a limited example, demo, or proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
"[![license](https://img.shields.io/badge/license-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)"
"[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/regions)](https://cran.r-project.org/package=eurobarometer)"
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.3825700.svg)](https://doi.org/10.5281/zenodo.3825700)
<!-- badges: end -->

@@

The SPSS files in GESIS are not ready for programmatic use in R, because the variable names often contain reserved special characters. You should use `gesis_metadta_create()` to understand what are the possible problems in the SPSS file and how to resolve them. (See: [Working With Metadata](http://eurobarometer.danielantal.eu/articles/metadata.html))

@@

* You can read in the SPSS file to R in haven, which will result in many `labelled` variables. The metadata file contains a suggestion of the most practical class conversion for data analysis. You can review and change this suggestion and then make the conversions at once with `convert_class()`

@@

*  The regional boundaries are consistently used, coded and named - this will be harmonized with the package `regions` , currently under review in CRAN, which will help resolving common issues, and to properly join various Eurobarometer files with Eurostat data tables and Google data tables.

>>>>

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/antaldaniel/eurobarometer/branch/master/graph/badge.svg)](https://codecov.io/gh/antaldaniel/eurobarometer?branch=master)
[![Project Status: Minimal or no implementation has been done yet, or the repository is only intended to be a limited example, demo, or proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
"[![license](https://img.shields.io/badge/license-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)"
"[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/regions)](https://cran.r-project.org/package=eurobarometer)"
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.3825700.svg)](https://doi.org/10.5281/zenodo.3825700)
[![Follow author](https://img.shields.io/twitter/follow/antaldaniel.svg?style=social)](https://twitter.com/intent/follow?screen_name=antaldaniel)

<!-- badges: end -->

@@

The SPSS files in GESIS are not ready for programmatic use in R, because the variable names often contain reserved special characters. You should use `gesis_metadata_create()` to understand what are the possible problems in the SPSS file and how to resolve them. (See: [Working With Metadata](http://eurobarometer.danielantal.eu/articles/metadata.html))

@@

* You can read in the SPSS file to R in [haven](https://haven.tidyverse.org/), which will result in many `labelled` variables. The metadata file contains a suggestion of the most practical class conversion for data analysis. You can review and change this suggestion and then make the conversions at once with `convert_class()`

See `vignette("metadata")`

@@

*  The regional boundaries are consistently used, coded and named - this will be harmonized with the package [regions](http://regions.danielantal.eu/), which helps resolving common issues, and to properly join various Eurobarometer files with Eurostat data tables and Google data tables.
